Compositional equivalences based on Open pNets

### 2020-05-19 2016-Weak-FH-Bisim/WeakBisim.tex
small edits before pulling...

\TODO{Ludo: add positioning wrt FORTE (variables)}

@@

@@

We are currently extending this work,  looking at  both further properties of 
FH-bisimulation, but also
the relations with existing equivalences on closed systems.
We also plan to apply open pNets to the study of complex composition
operators in a symbolic way, for example in the area of parallel
skeletons, or distributed algorithms.
We have developped tool support for computing the
symbolic semantics in term of open-automata \cite{QBMZ-AVOCS18}, and have
developed algorithms to check strong FH-bisimulation \cite{hou:hal-02406098}.

\ERIC{
  =>  Expliquer deux versions algos bisim (check/on-the-fly)\\
=> Do we need comment on Simplification ? I'm not sure I can write
something definitive, and Zechen is currently working on it.\\
=> idees pour implementer Weak efficacement (= sans construire WOA) ?}

\TODO{Further work: Branching ? Refinements ? }

@@

This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible with the right side conditions. 
\qedhere
\end{itemize}
\end{proof}

@@

 We can decompose each of the $n+1$ subsequences in the following way (see Figure~\ref{figproof}).
For $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$. For $l\in [1..n]$,  $n'_l$ is any index between $n_{l-1}$ and $n_l$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$. We obtain $n+1$ subsequences  made of the following OTs, for all $k\in [0..n]$ :\\
\begin{small}
$\forall p\! \in\! [n'_{k}..(n_k\!-\!1)]~ Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
				{{\Post\,''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,\quad
Q\models{\openrule
			{
				\beta_{n_k j}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{n_k}}},  
				{{\Post\,''_{n_k}}}}
				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha_{{n_k}}}
				\ostate{v_{(n_k+1)l}^{l\in L_Q}}}
				}%\]
$
\end{small}
and\\
\begin{small}
$\forall p \in [(n_k\!+\!1)..(n'_{k+1}\!-\!1)]\,\, Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
				{{\Post\,''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$
\end{small}
\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
				{{\Post_k}}}
			{\ostate{v_{kl}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
				\ostate{(v_{kl}')^{l\in L_Q}}}
		}%\]
\end{mathpar}
With:
{\small
\begin{align*}
\forall l \in L_Q. &v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}\\
\alpha_k'=&\alpha_{n_k}{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}\\
{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=&{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
&\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post\,''_{l}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}} }\\
\Pred_k=&\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\Pred\,''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\\ 
&\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post\,''_{j}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{j}}
\\
\Post_k= &\bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post\,''_{j}
\end{align*}
}

@@

We need now to show that the set of WOT obtained above verifies the conditions of the lemma, i.e. it is a set of WOT of the form:
\[	Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}\]
With
\[  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad\text{trivial}\]
\[ \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i)}\]
Indeed we have:
\begin{equation*}
\begin{split}
\gamma_j^{j\in J}=&\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\! \Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup\\& \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }\\
\end{split}\end{equation*}

@@

$\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i$ (see above):\\

@@

Next, we have
\[\Pred = \displaystyle{\Pred\,'
		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )}\]

@@

\begin{scriptsize}
\begin{align*}

@@

		\land {\Pred\,''_{3i}}\land \alpha_{3i}=\beta_{3ij_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\displaybreak[0]\\

@@

\end{align*}
\end{scriptsize}
which is exactly what is needed.

@@

{\small \begin{align*}

@@

&=\Post\,' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post\,''_{j}\qedhere
\end{align*}}

@@

\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose1} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
	Suppose $j_0\in J$  and:\\[-1ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\beta_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
		\ostate{(s_i')^{\, i\in L}}}
}
\quad\text{~~and~~}\quad
Q\models{\openrule
	{
		\set{\gamma},
		 \Pred_Q,  
		\Post_Q}
	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
		\ostate{(s'_{i})^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Let 
%J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
\qquad
$\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q) \quad\text{~~and~~}\quad
%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
\Post\,'=\Post\uplus\Post_Q
$

Then, we have
{\small	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}, 
			\Pred\,',  \Post\,'
			 }
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
	}
	\]}
\end{lemma}
\begin{proof}
By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an $\alpha'_Q$ open transition (that can be observable or not depending on $\alpha_Q$):
\begin{mathpar}
\forall h\!\in\![0..k].Q\models\openrule
    {\set{\beta_{1h}},\Pred_{1h},\Post_{1h}   }
         {\ostate{{(s_{1h})}} \OTarrow {\tau} \ostate{{(s_{1(h+1)})}}}, \quad
Q\models{\openrule
	{
		\set{\beta_2},
		 \Pred_2,  
		\Post_2}
	{\ostate{s_{20}}\OTarrow {\alpha'_Q}
		\ostate{s_{21}}}
}, \\ \quad\text{~~and~~}\quad 
\forall h \in [0..k'].Q\models\openrule
         {
           \set{\beta_{3h}},\Pred_{3h}, \Post_{3h}}
         { \ostate{(s_{3h})} \OTarrow {\tau} \ostate{(s_{3(h+1)})}}
\end{mathpar}
such that\\

@@

\item For the possibly observable open transition.  By Lemma \ref{lem-compose} with the lemma hypotheses we obtain:\\ 
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}, 
			\Pred\land\Pred_2\land \alpha_Q=\beta_{j_0 },  
			\Post\uplus \Post_2}
{\ostate{s^{i\in L}_{i}\uplus s_{20}} \OTarrow {\alpha} \ostate{{s'}^{i\in L}_{i}\uplus s_{21}}}
	}
	\]

@@

Using Lemma \ref{lem-rel-OT-WOT}, from cases $(1)$, $(2)$ and $(3)$ we get: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
\set{\gamma_c}, \Pred_c,
\Post_c}
         {\ostate{s_{10}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha'} 
	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
where ~~
$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$
and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.
\begin{small}
\begin{align*}
\set{\gamma_c}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{i=h-1}^{0}\!\! \Post_{1i} } }  \dotcup  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigotimes_{i=k}^{0}\Post_{1i}}} \dotcup\\
&\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{i=h-1}^{0}\!\!\Post_{3i}\shortotimes\Post_2\shortotimes\bigotimes_{i=k}^{0}\Post_{1i}} }\\
=&\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad  \text{ because $\Post_{1j}$  does not act on variables of $\beta_j$.}  
\displaybreak[0]\\
\Pred_c=&
\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_{1i}}\land
\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0}\right) \subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\
&\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
\\
\Post_c=&(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}
\end{align*}
\end{small}
\noindent Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$.

Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on  variables of $Q$. We conclude on predicate and posts as follows\footnote{$\Post_{1i}$ only has an effect on variables of $Q$ and thus does not modify $\Pred$ or $\beta_{j_0}$}:
\begin{equation*}
\begin{split}
\Pred_c&=\Pred_Q\land\Pred\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land
(\alpha'_Q=\beta_{j_0})\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\\
&=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}\\[.3ex]
\Post_c&=\Post\uplus\Post_Q \qedhere
\end{split}
\end{equation*}
\end{proof}
\smallskip
\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}). Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\gamma_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}
\qquad\text{~~and for all $p\in[0..n]$~~}\quad
Q\models{\openrule
	{
		\gamma_{pj}^{j\in J_p},
		 \Pred_p,  
		\Post_p}
	{\ostate{s_{pi}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
}%\]
\end{mathpar}

Let 
\begin{mathpar}
J_Q=\displaystyle{\bigcup_{p=0}^nJ_{p}}

\forall{i\in L_Q}.\,s_i=s_{0i}~~\land~~s'_i=s_{(n+1) i}

\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}\subst{\bigotimes_{k=p}^{0}{\Post_k}}}

\Pred\,'=\Pred\land \bigwedge_{p=0}^{n}(\alpha_t=\beta_t\land \Pred_t)\bigotimes_{i=p-1}^{0}\Post_i

>>>>

@@

\paragraph{Proving bisimulation in practice}

@@

We are currently extending this work,  looking at  both further properties of 
FH-bisimulation, but also
the relations with existing equivalences on closed systems.
We also plan to apply open pNets to the study of complex composition
operators in a symbolic way, for example in the area of parallel
skeletons, or distributed algorithms.
We have developped tool support for computing the
symbolic semantics in term of open-automata \cite{QBMZ-AVOCS18}, and have
developed algorithms to check strong FH-bisimulation \cite{hou:hal-02406098}.  
Naturally we are now working toward an implementation of weak FH-Bisimulation. 
The challenges here, in the context of uour symbolic systems, is not so much algorithmic complexity,
as was the case with classical weak bisimulation on finite models, but decidability and termination.
Two main directions should be explored, either with an explicite construction of the weak transition, but this step in
itself may introduce non-termination, or a direct implementation of the weak bisimulation definition, without
constructing the weak automaton. We can expect that optimisations here in the symbolic setting would be quite different from the classical case.

@@

This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible with the right side conditions. 
\end{itemize}
\end{proof}

@@

 We can decompose each of the $n+1$ subsequences in the following way (see Figure~\ref{figproof}).
For $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$. For $l\in [1..n]$,  $n'_l$ is any index between $n_{l-1}$ and $n_l$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$. We obtain $n+1$ subsequences  made of the following OTs, for all $k\in [0..n]$ :\\
\begin{small}
$\forall p\! \in\! [n'_{k}..(n_k\!-\!1)]~ Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
				{{\Post\,''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,\quad
Q\models{\openrule
			{
				\beta_{n_k j}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{n_k}}},  
				{{\Post\,''_{n_k}}}}
				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha_{{n_k}}}
				\ostate{v_{(n_k+1)l}^{l\in L_Q}}}
				}%\]
$
\end{small}
and\\
\begin{small}
$\forall p \in [(n_k\!+\!1)..(n'_{k+1}\!-\!1)]\,\, Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
				{{\Post\,''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$
\end{small}
\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
				{{\Post_k}}}
			{\ostate{v_{kl}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
				\ostate{(v_{kl}')^{l\in L_Q}}}
		}%\]
\end{mathpar}
With:
$\forall l \in L_Q. v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}$\\
$\alpha_k'=\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}$\\
$\displaystyle{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=\displaystyle{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
{}~~\qquad \qquad\qquad\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post\,''_{l}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}} }\\
%
\Pred_k=\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\Pred\,''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\\ 
{}~\qquad\quad\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post\,''_{j}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{j}}
\\
\Post_k= \bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post\,''_{j}$\\

@@

We need now to show that this set of WOT verifies the conditions of the lemma, i.e. it is a set of WOT of the form:
\[	Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}\]
With
\[  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad\text{trivial}\]
\[ \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i)}\]
Indeed we have:
\begin{equation*}
\begin{split}
\gamma_j^{j\in J}=&\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\! \Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup\\& \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }\\
\end{split}\end{equation*}

@@

$\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i$ (see above)\\

@@

$\Pred = \displaystyle{\Pred\,'
		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )}$\\

@@

\begin{equation*}

@@

		\land {\Pred\,''_{3i}}\land \alpha_{3i}=\beta_{3ij_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\

@@

which is exactly what is needed.\\

@@

\begin{equation*}

@@

&=\Post\,' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post\,''_{j}
\end{split}
\end{equation*}

@@

\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose1} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
	Suppose $j_0\in J$  and:\\[-1ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\beta_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
		\ostate{(s_i')^{\, i\in L}}}
}
\quad\text{~~and~~}\quad
Q\models{\openrule
	{
		\set{\gamma},
		 \Pred_Q,  
		\Post_Q}
	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
		\ostate{(s'_{i})^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Let\\[-3ex] 
\begin{mathpar}
%J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
%\qquad
\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q) \quad\text{~~and~~}\quad
%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
\Post\,'=\Post\uplus\Post_Q
\end{mathpar}
Then, we have\\[-3ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}, 
			\Pred\,',  \Post\,'
			 }
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\begin{proof}
By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an observable open transition:
\begin{mathpar}
\forall h\!\in\![0..k].Q\models\openrule
    {\set{\beta_{1h}},\Pred_{1h},\Post_{1h}   }
         {\ostate{{(s_{1h})}} \OTarrow {\tau} \ostate{{(s_{1(h+1)})}}}, \quad
Q\models{\openrule
	{
		\set{\beta_2},
		 \Pred_2,  
		\Post_2}
	{\ostate{s_{20}}\OTarrow {\alpha'_Q}
		\ostate{s_{21}}}
}, \\ \quad\text{~~and~~}\quad 
\forall h \in [0..k'].Q\models\openrule
         {
           \set{\beta_{3h}},\Pred_{3h}, \Post_{3h}}
         { \ostate{(s_{3h})} \OTarrow {\tau} \ostate{(s_{3(h+1)})}}
\end{mathpar}
such that\\

@@

\item For the observable open transition.  By Lemma \ref{lem-compose} with the lemma hypotheses we obtain:\\ 
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}, 
			\Pred\land\Pred_2\land \alpha_Q=\beta_{j_0 },  
			\Post\uplus \Post_2}
{\ostate{s^{i\in L}_{i}\uplus s_{20}} \OTarrow {\alpha} \ostate{{s'}^{i\in L}_{i}\uplus s_{21}}}
	}
	\]

@@

Using Lemma \ref{lem-rel-OT-WOT}, from cases $(1)$, $(2)$ and $(3)$ we get: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
\set{\gamma_c}, \Pred_c,
\Post_c}
         {\ostate{s_{10}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha'} 
	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
where ~~
$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$
and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.\\
$\displaystyle{
\set{\gamma_c}=\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{i=h-1}^{0}\!\! \Post_{1i} } }  \dotcup  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigotimes_{i=k}^{0}\Post_{1i}}} \dotcup}$ \\ 
${}~~\hspace{1.8em}\displaystyle{\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{i=h-1}^{0}\!\!\Post_{3i}\shortotimes\Post_2\shortotimes\bigotimes_{i=k}^{0}\Post_{1i}} }}$\\
${}~~\hspace{0.6em}=\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad$  because $\Post_{1j}$  does not act on variables of $\beta_j$.  \\
\begin{small}
$\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_{1i}}\land
\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\\displaystyle
\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
\end{array}
$\\
$\Post_c=\displaystyle{(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}$
\end{small}

\noindent Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$.

Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on state variables of $Q$. We conclude on predicate and posts as follows\footnote{$\Post_{1i}$ only has an effect on variables of $Q$ and thus does not modify $\Pred$ or $\beta_{j_0}$}:
\begin{equation*}
\begin{split}
\Pred_c&=\Pred_Q\land\Pred\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land
(\alpha'_Q=\beta_{j_0})\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\\
&=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}\\[.3ex]
\Post_c&=\Post\uplus\Post_Q \\[-3ex]
\end{split}
\end{equation*}
\end{proof}

\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}). Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\gamma_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}\\
\text{~~and for all $p\in[0..n]$~~}
Q\models{\openrule
	{
		\gamma_{pj}^{j\in J_p},
		 \Pred_p,  
		\Post_p}
	{\ostate{s_{pi}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
}%\]
\end{mathpar}
